Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
review introduction

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

%% \textcolor{red}{Cristina: Can you please further expand the introduction
%% by adding more details about our synthesis approach to control systems?}

@@

\todo{We should briefly describe both approaches that we have implemented.}

%-------------------------------
\subsection{Related work}
\label{sec:relw}
%-------------------------------

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. Note that, 
as mentioned at the beginning of the section, 
we consider the reference signal to be 0.
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$.

We compute the coefficients for $K$ 
in the domain $\mathbb{R}<I,F>$.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{In the second approach,...}

\textcolor{red}{we have to connect both paragraphs...}

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of abstraction refinement in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.

@@

%-------------------------------
\section{Related work}
\label{sec:relw}
%-------------------------------

@@
